Draft of paper

### 2024-12-12 Paper draft/draft.tex
Testo simulazioni fatto

By adding these constraints we obtain some desirable performances upgrade:
\begin{itemize}
  \item By minimizing the trace of $P$ we are maximizing the volume of the ellipsoid $\cE(P, x_*)$ hence the ROA.
  \item By minimizing the trace of $\Sigma$ we are minimizing the conservatism of the controller by obtaining a constraint matrix $\Xi$ directly related to the decay rate of the Lyapunov function as close to zero as possible but never greater due to the second condition in \eqref{eqn:optimization}.
  \item By taking \eqref{eqn:optimization} and applying the Schur complement to the last condition we obtain
  $$
  X^i {X^i}\tr \leq \beta_i \Id
  $$
  meaning that the smaller the value of $\beta_i$ the smaller will be the value that appears directly in the ETM triggering condition \eqref{eqn:etm-trigger} hence the lower the number of events.
\end{itemize}

@@

\section{Simulations}

>>>>

{\color{red}{Mi fa cagare l'espressione della minimizzazione così}}

By adding these constraints we obtain some desirable performances upgrade:
\begin{itemize}
  \item By minimizing the trace of $P$ we are maximizing the volume of the ellipsoid $\cE(P, x_*)$ hence the ROA.
  \item By minimizing the trace of $\Sigma$ we are minimizing the conservatism of the controller by obtaining a constraint matrix $\Xi$ directly related to the decay rate of the Lyapunov function as close to zero as possible but never greater due to the second condition in \eqref{eqn:optimization}.
  \item By taking \eqref{eqn:optimization} and applying the Schur complement to the last condition we obtain
  $$
  X^i {X^i}\tr \leq \beta_i \Id
  $$
  meaning that the smaller the value of $\beta_i$ the smaller will be the value that appears directly in the ETM triggering condition \eqref{eqn:etm-trigger} hence the lower the number of events.
\end{itemize}
{\color{red}{Vorrei migliorare questa parte}}

@@

\section{Simulations}
We considered an inverted pendulum system with mass $m = 0.15 kg$, length $l = 0.5 m$, damping coefficient $\mu = 0.05 N ms/rad$, gravitational acceleration $g = 9.81 m/s^2$ and the addition of an integrator in its dynamics. The DT model of the system is given with respect to \eqref{eqn:system-dynamics} by:
\begin{equation}\label{eqn:pendulum}
\begin{aligned}
  &x = \bmx{\theta \\ \dot{\theta} \\ z} \quad 
  A = \bmx{1 & dt & 0\\
  \frac{g}{l} dt & 1 - \frac{\mu}{m l^2} dt & 0\\
  1 & 0 & 1}\quad
  B = \bmx{0\\ \frac{\bar{\tau}}{m l^2} dt\\ 0} \\
  &C = \bmx{0 \\ \frac{g}{l} dt \\ 0} \quad
  D = \bmx{0 \\ 0 \\ -1} \quad
  E = \bmx{1 & 0 & 0}
\end{aligned}
\end{equation}
With the maximum torque available $\bar{\tau} = 5 N m$, the sampling time $dt = 0.02 s$ and the non-linearity $\Phi(Ex) = \text{sin}(Ex) - Ex$. We have trained a stabilizing NN controller with Reinforcement Learning (RL) structured as an MLP of $3$ layers with $n_{\phi_1} = n_{\phi_2} = n_{\phi_3} = 32$. The addition of the integrator in the system dynamics made the training less trivial and allowed to compensate the intrinsic equilibrium points given by the controller that are generally different from the origin. The output of the controller $\bar{u}$ is a scalar, the saturation level $\hat{u}$ of the last ETM (see fig. \ref{fig:second_scheme}) is set to $1$ given the nature of RL training that always normalizes the final output of the network. We solved many instances of the LMI problem by first applying the ETM with null threshold, dynamic threshold, new ETM triggering matrices found with Lemma \ref{lem:finsler} and finally the matrices that we obtained by the application of Corollary \ref{cor:optimization} observing a considerable upgrade in performances in terms of computational saving. The results are shown in the following table:

{\color{red}{Troppo discorsivo?}}
